---
title: "ProblemSet6"
author: Arthur Hernandez
output: html_document
---

##Problem Set 6
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
pulses <- scan("https://mtrosset.pages.iu.edu/StatInfeR/Data/pulses.dat")
```
```{r}
sample <- scan("https://mtrosset.pages.iu.edu/StatInfeR/Data/sample774.dat")
```
```{r}
summary(pulses)
```
Question #2
part a:
```{r}
plot(ecdf(pulses), main = "Empirical CDF for Peruvian Indian Pulses",xlab = "Pulse rate")
```

part b:
```{r}
mean(pulses)
```
```{r}
mean((pulses - mean(pulses))^2)
var(pulses)
```

part c:
```{r}
median(pulses)
```
```{r}
IQR(pulses)
```

part d:
```{r}
IQR(pulses)/sqrt(var(pulses))
```

part e:
```{r}
boxplot(pulses,ylab = "Pulse Rate", main = "Box Plot of Peruvian Indian Pulse Rates")
```

part f:
```{r}
qqnorm(pulses,ylab = "Pulse Rate", xlab = "Theorectial Quantity",main = "Normal Probability Plot of Peruvian Indian Pulse Rates")
```

part g:
```{r}
plot(density(pulses), main = "Density Plot for Peruvian Indian Pulses",xlab = "Pulse rate")
```

part h:
This sample was not drawn from a normal distribution. the QQ plot is not close to being a straight line.

Question #3

part a:
```{r}
plot(ecdf(sample),main = "Empirical CDF Graph For Peruvian Indian Pulses",xlab = "Pulse Rate")
```

part b:
```{r}
#mean
mean(sample)
var(sample)
median(sample)
IQR(sample)
```

part c:
```{r}
sqrt(var(sample))
IQR(sample)

```

part d:
```{r}
plot(qqnorm(sample), main = "Normal Prbability Plot For Some Sample",ylab = "Sample quantities",xlab = "Theoretical Quantities")
```

No, I do not think x-> was drawn from a normal distribution. The distribution is not linear.

part e:
```{r}
plot(qqnorm(log(sample)), main = "Normal Prbability Plot For Some Sample",ylab = "Sample Quantities", xlab = "Log of theoretical Quantities")
```

I believe that with more data, this distribution would be a normal distribution. The graph is close to linear.

Question 4:

part a:

E(x) = ((-2) * 0.3) + ((-1) * 0.6) + (12 * 0.1) = 0

part b:

V(x) = ((-2)^2 * 0.3) + ((-1)^2 * 0.6) + (12^2 * 0.1) = 1.2 + .6 + 14.4 = 16.2

part c:

since E(´x) = E(x), E(´x) = 0

part d:
Var(x) = Varx/100 = .162

part e:
```{r}
1-pnorm(.5,0,sqrt(0.162))
```
